DATA 621 - Business Analytics and Data Mining

### 2020-12-13 Final_project/Final Project Paper - Group 2.Rmd
copyediting

### Numeric Predictors
For numeric predictors, we are using the number of `likes`, `dislikes`, `tags`,
and `comments`. We may also consider the country of viewing as well. From the 
There is not that much difference in the distribution of the numeric predictors
between the countries where people view.

@@

```{r catPlot, fig.height=4.5, fig.width=8}
ggplot(usSetF[measure == 'category'], aes(y = value)) +
  geom_bar() +
  ggtitle("Distribution by Category") +
  scale_x_continuous(labels = comma)
```

>>>>

### Numeric Predictors
For numeric predictors, we are using the number of `likes`, `dislikes`, `tags`,
and `comments`.

@@

```{r catPlot, fig.height=4.5, fig.width=8}
ggplot(usSetF[measure == 'category'], aes(y = value)) +
  geom_bar() +
  ggtitle("Distribution by Category: United States") +
  scale_x_continuous(labels = comma)
```
